---
title: "Time Series Analysis in the Financial Market"
author: "Caio di Felice Cunha"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

<!--
NOTE: This R Markdown source was reconstructed from the committed standalone
script ("Time Series Analysis in the Financial Market.R") and the chunk order
visible in the committed PDF. It has NOT been re-knitted on this machine (no R
environment available), so it is provided as a best-effort reproducible source.
Re-knit it in R/RStudio to verify it reproduces the report.
-->

## Overview

Time series analysis of a Berkshire Hathaway B-share listing using `quantmod`.
Reference: http://www.quantmod.com

Data caveat: the ticker `BRKB.VI` is the Vienna (VIE) EUR cross-listing, which is
very thinly traded. Volume and ADX readings are computed on illiquid quotes and
should be read with caution. The canonical liquid listing is `BRK-B` on the NYSE.

```{r packages}
# install.packages("quantmod")
# install.packages("xts")
# install.packages("moments")
library(quantmod)
library(xts)
library(moments)
```

## Stage 1 - Download the data

```{r download}
startDate <- as.Date("2023-01-01")
endDate   <- as.Date("2023-04-04")

getSymbols("BRKB.VI", src = "yahoo", from = startDate, to = endDate, auto.assign = TRUE)

class(BRKB.VI)
is.xts(BRKB.VI)
head(BRKB.VI)
```

## Stage 2 - Closing prices

```{r closing}
BRKB.VI.Close <- BRKB.VI[, 'BRKB.VI.Close']
is.xts(BRKB.VI.Close)
head(Cl(BRKB.VI), 5)
```

## Stage 3 - Charts and indicators

Candlestick chart of the listing.

```{r candle}
candleChart(BRKB.VI)
```

Daily closing price.

```{r close-plot}
plot(BRKB.VI.Close, main = "Daily Closing Berkshire Hathaway Inc. Shares",
     col = "red", xlab = "Date", ylab = "Price", major.ticks = 'months',
     minor.ticks = FALSE)
```

Bollinger Bands (20-period mean, 2 standard deviations). The candlestick chart is
redrawn first because `addBBands()` overlays on the last `chartSeries` object.

```{r bbands}
candleChart(BRKB.VI)
addBBands(n = 20, sd = 2)
```

ADX trend indicator (11-period EMA).

```{r adx}
addADX(n = 11, maType = "EMA")
```

## Stage 4 - Calculating some statistical measures

Daily log returns.

```{r returns}
BRKB.VI.ret <- diff(log(BRKB.VI.Close), lag = 1)

# Remove the leading NA from differencing
BRKB.VI.ret <- BRKB.VI.ret[-1]

plot(BRKB.VI.ret, main = "Daily Closing of Berkshire Hathaway Inc. Shares",
     col = "red", xlab = "Date", ylab = "Return", major.ticks = 'months',
     minor.ticks = FALSE)
```

Summary statistics of the daily log returns.

```{r stats}
statNames <- c("Mean", "Standard Deviation", "Skewness", "Kurtosis")
BRKB.VI.stats <- c(mean(BRKB.VI.ret), sd(BRKB.VI.ret),
                   skewness(BRKB.VI.ret), kurtosis(BRKB.VI.ret))
names(BRKB.VI.stats) <- statNames
BRKB.VI.stats
```

## Stage 5 - Save the data

```{r save}
saveRDS(BRKB.VI, file = "BRKB.VI.rds")
Ptr <- readRDS("BRKB.VI.rds")
head(Ptr)
```
